Evolution of the AGN UV luminosity function from redshift 7.5

### 2018-06-08 Paper/paper.tex
Update Section 1

The luminosity function of active galactic nuclei (AGN) and its
evolution over cosmological time scales has been a matter of central
interest of a large body of work over the last four decades
\citep[e.g.,][]{1978A&A....68...17M, 1983ApJ...269..352S,
  1988ApJ...325...92K, 1988MNRAS.235..935B, 1993ApJ...406L..43H,
  1994ApJ...421..412W, 1995AJ....110...68S, 1995AJ....110.2553K,
  1995ApJ...438..623P, 2000MNRAS.317.1014B, 2001AJ....121...54F,
  2004AJ....128..515F, 2006AJ....131.2766R, 2007ApJ...654..731H,
  2009MNRAS.392...19C, 2010AJ....139..906W, 2011ApJ...728L..26G,
  2013ApJ...773...14R, 2013ApJ...768..105M, 2015AA...578A..83G,
  2015ApJ...798...28K, 2016ApJ...829...33Y, 2016ApJ...833..222J,
  2017MNRAS.466.1160M}.  Determination of the AGN luminosity function
constrains models of the build-up of supermassive black holes
\citep{2015MNRAS.452..575S, 2016MNRAS.462..190R}.
%% JFH Some historical papers should be cited for this SMBH buildup point, like
%% for example Soltan. 
Due to the
incidence of supermassive black holes in most galaxies, the tight
scaling relations observed to exist between the mass of these black
holes and properties of their host galaxies
\citep{2013ARA&A..51..511K, 2013ApJ...764..184M}, and the increasing
consensus that AGN activity feeds back on the host galaxy evolution,
the AGN luminosity function also constrains models of galaxy
formation.  Finally, thanks to their relative brightness and high
Lyman-continuum (LyC) escape fractions, the luminosity function of AGN
determines their influence on the temperature and ionization state of
the intergalactic medium (IGM) over large scales,
%% JFH Probably want to say something here about radiation background
%% instead of this ``large scales'' 
possibly even
primarily driving hydrogen and helium reionization.

There is a renewed interest in understanding the evolution of the UV
luminosity function of AGN, triggered by the 19 low-luminosity
($M_{1450}>-22.6$)
%% JFH Probably more sensible to quote a luminosity range rather than just a > 
AGN candidates between redshifts $z=4.1$ and $6.3$
discovered by \citet{2015AA...578A..83G} using a novel X-ray/NIR
selection criterion.  This finding suggested that AGN brighter than
$M_{1450}=-18$ can potentially produce all of the metagalactic
hydrogen photoionization rate inferred from the \lya forest at
$4<z<6$.
%% JFH Probably should say something here about assuming all ionizing photons escape, since these
%% are galaxy like luminosities. Maybe quote L_star galaxy for comparison, which helps with your next
%% point about faint galaxies. 
A significant presence of AGN at high redshift ($z\sim 6$)
and a dominant contribution of AGN to reionization is appealing as the
LyC escape fraction of galaxies is uncertain.  High-redshift galaxies
down to rest-frame UV magnitude $M_\mathrm{UV}=-12.5$ ($L\sim
10^{-3}L^*$) at $z=6$ \citep{2017ApJ...835..113L} and redshifts up to
$z=11.1$ \citep{2016ApJ...819..129O} have now been reported.  But the
escape of LyC photons has been measured in only a few comparatively
bright ($L>0.5L^*$) galaxies at relatively low redshifts ($z < 4$).
The escape fraction in these galaxies is inferred to be typically
about 2--20\% \citep{2010ApJ...725.1011V, 2011ApJ...736...41B,
  2015ApJ...804...17S, 2015ApJ...810..107M, 2016A&A...585A..48G,
  2017MNRAS.468..389J, 2017MNRAS.465..316M}, whereas reionization
requires escape fraction of about 20\% in galaxies as faint as
$M_\mathrm{UV}=-13$ \citep{2016PASA...33...37F, 2015ApJ...802L..19R,
  2016MNRAS.457.4051K}.  An enhanced incidence of high-redshift AGN
may also be consistent with the shallow bright-end slopes of the
$z\sim 7$ UV luminosity function of galaxies relative to a Schechter
function \citep{2012MNRAS.426.2772B, 2014MNRAS.440.2810B,
  2014ApJ...792...76B, 2015MNRAS.452.1817B} and the hard spectra of
these galaxies \citep{2015MNRAS.450.1846S, 2015MNRAS.454.1393S,
  2017MNRAS.464..469S}.  Finally, AGN may also provide a natural
explanation for the large scatter in the \lya opacity between
different quasar sightlines close to redshift $z=6$
\citep{2015MNRAS.447.3402B, 2018arXiv180208177B}.
%% JFH Please cite new paper by eilers et al. here, not yet on archive. 
These opacity
fluctuations extend to substantially larger scales ($\gtrsim 50\,
h^{-1}$cMpc) than expected in galaxies-dominated reionization models
\citep{2015MNRAS.453.2943C}.
%% JFH You probably need a ``but see Davies et al. 201X'' since Fred claims
%% he can explain these fluctuations with galaxies. See also the new paper with George Becker and Fred. 
AGN clustering can result in these
fluctuations naturally if there is a significant contribution
($\gtrsim 50\%$) of AGN to the ionising emissivity at $z=5$--$6$
\citep{2017MNRAS.465.3429C}.

Several counter-arguements against a higher incidence of AGN at high
redshift have also been made. \citet{2017MNRAS.468.4691D} and
\citet{2018MNRAS.473.1416M} pointed out that an AGN population
consistent with the findings of \citet{2015AA...578A..83G} leads to a
much earlier \HeII\ reionization.  For instance, in the model of
\citet{2015ApJ...813L...8M}, He~\textsc{ii} reionization is complete
at $z=4.5$, compared to $z=3$ in the standard scenario
\citep{2012ApJ...746..125H}.  Such early \HeII\ reionization could
result in higher IGM temperatures due to the associated photoheating.
\citet{2017MNRAS.468.4691D} found that the temperature of the IGM at
mean density is twice as much in AGN-dominated reionization models as
the standard models at $z=3.5$--$5$, in conflict with constraints from
the \lya forest.  This inconsistency could be avoided by postulating a
reduced escape fraction of \HeII-ionizing photons in AGN, but it is
difficult to reconcile this with a unit escape fraction of
hydrogen-ionizing photons that is required to explain the Ly$\alpha$
opacity fluctuations.
%% JFH Probably need to clarify for this last point that you mean in a situation
%% where galaxies contribute no LL photons, and QSOs completely dominate. 
Further arguments against AGN-dominated
reionization have been presented by \citet{2016MNRAS.459.2299F} by
analysing the incidence of metal-line absorbers at $z\sim 6$.
\citet{2016MNRAS.459.2299F} find that in their cosmological radiation
hydrodynamical simulations AGN-dominated UV background results in too
many C~\textsc{iv} absorption systems relative to Si~\textsc{iv} and
C~\textsc{ii} at $z\sim 6$.  However, these simulations assume a
$L_\nu\propto\nu^{-1.57}$ AGN SED at extreme UV
\citep{2002ApJ...565..773T}, which somewhat harder than recent
measurements ($L_\nu\propto\nu^{-1.7}$) by
\citet{2015MNRAS.449.4204L}.  \citet{2016MNRAS.459.2299F} also found
that the N(Si~\textsc{iv})/N(C~\textsc{iv}) column density ratio
measurements prefer a harder and more intense $>4$~Ry background than
the standard model \citep{2012ApJ...746..125H}.  Finally, comparing
the \citet{2015AA...578A..83G} sample to X-ray-selected quasar data at
$z=0$--$6$, \citet{2017MNRAS.465.1915R} argued that the faint end of
the AGN UV luminosity function at $z\sim 6$ is probably shallower that
that reported by \citet{2015AA...578A..83G}.
\citet{2017MNRAS.465.1915R} argue that the apparent contradiction with
the results of \citet{2015AA...578A..83G} could be explained by
contamination from the AGN host galaxies for faint AGN.

While a straightforward way towards a more robust understanding of AGN
contribution to reionization is to determine the evolution of the AGN
UV luminosity function, many recent inferences of the luminosity
function suffer from inconsistencies arising from inhomogeneous
selection and mixing of AGN data.  This has resulted in a large
scatter in the inferred high-redshift hydrogen-ionizing AGN emissivity
between various recent studies.  For instance, there is an order of
magnitude scatter between various estimates of the hydrogen-ionizing
AGN emissivity at $z=5$--$6$ \citep{2011ApJ...728L..26G,
  2012ApJ...755..169M, 2015AA...578A..83G, 2018PASJ...70S..34A,
  2018AJ....155..131M, 2018MNRAS.474.2904P, 2017ApJ...847L..15O,
  2017MNRAS.466.1160M}.  Our aim in this paper is to address this
issue, by constructing an AGN sample with robust redshift and
completeness estimates and homogeneous assumptions of the cosmology
and intrinsic AGN spectrum.  We discuss our sample construction in
Section~\ref{sec:sample}.  Our derived luminosity functions are
presented in Section~\ref{sec:lf}.  Section~\ref{sec:reion} presents
our inference of the AGN contribution to hydrogen and helium
reionization.  We summarise our findings in Section~\ref{sec:conc}.

@@

Our estimates for the double power law luminosity function are shown
in Figure~\ref{fig:mosaic} for 25 redshift bins.
%% JFH you are confusing terminology. posterior median and best-fit are not generally the same and you should
%% not refer to them as such. You are also not explaning what you mean by posterior median. Is this the
%% median of the individual marginalized posteriors? Or is it the median of the function that results from
%% the posterior distribution? Those are not generally the same, unless the model is linear in the parameters,
%% which it is not. Finally, best fit always means maximum likelihood, and that is certainly not what you are
%% plotting here, so don't say best-fit. You can say as our ``adopted model'' or ``fiducial model fit'' or
%% something like that. I would just explain waht you plot. 
The posterior median is shown as our adopted model at each redshift,
while the grey shaded region shows the one-sigma (68.26\%)
uncertainty.  Consistent with previous studies, the double power law
model provides an excellent description of the luminosity function
model over almost the complete range of redshifts spanned by the data.
It is only in the highest redshift bin ($z=5.5$--$6.5$) that the data
seem to favour a single power law.  In this bin, the resultant
posterior distribution of the break magnitude $M_*$ is bimodal with
favoured values at the faint ($M_*>-18$) and bright end of the data
($M_*<-30$).  While in the literature the $z\sim 6$ AGN have been
assumed to lie on the bright end of the luminosity function
\citep[e.g.,][]{2016ApJ...833..222J}, a comparison with the luminosity
function at lower redshifts ($z<5.5$) suggests that these AGN should
instead be understood to describe the faint-end of a double power law.
%% JFH Okay so you need to be more clear here that what you mean is that the trend
%% from the plot is that M_star gets progressively brighter with redshift. This is not
%% obvious given what you write here. Indeed, it is not super obvious until one looks at FIgure 4, which
%% anyway has this prior already in it. 
Therefore, in light of the
low-redshift data, we use restricted priors in this
%% JFH Which redshift bin?? Make it more clear that this prior is put in to avoid bi-modal distributions
%% and it is informed by inspection of the lower redshift data. 
redshift bin: we
restrict the bright-end slope $\alpha$ to values less than $-4$,
%% JFH Something does not jive here, since the error bars you are showing on the high-z poitns cross
%% the -4 value of your prior? So either your prior is not a hard prior, or it is not exactly at -4
which
is equivalent to forcing $M_*$ to be at the bright end of the data.
Other parameters continue to have wide uniform priors.  This also
illustrates the importance of analysing the evolution of the QLF with
redshift.

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small_global.pdf}
    % mosaic.py 
  \end{center}
  \caption{Luminosity function estimates from $z=0.6$ to $6.5$.
    Similar to Figure~\ref{fig:mosaic}, the symbols show our inferred
    binned luminosity functions.  In each redshift bin, yellow curves
    show our fiducial double power law luminosity function model in
    that redshift bin.  Other curves show the three global evolution
    models.  Shaded regions show the one-sigma (68.26\%)
    uncertainties.}
  \label{fig:mosaic_global}
\end{figure*}

>>>>

The luminosity function of active galactic nuclei (AGN) and its
evolution over cosmological time scales has been a matter of central
interest of a large body of work over the last four decades
\citep{1978A&A....68...17M, 1983ApJ...269..352S, 1988ApJ...325...92K,
  1988MNRAS.235..935B, 1993ApJ...406L..43H, 1994ApJ...421..412W,
  1995AJ....110...68S, 1995AJ....110.2553K, 1995ApJ...438..623P,
  2000MNRAS.317.1014B, 2001AJ....121...54F, 2004AJ....128..515F,
  2006AJ....131.2766R, 2007ApJ...654..731H, 2009MNRAS.392...19C,
  2010AJ....139..906W, 2011ApJ...728L..26G, 2013ApJ...773...14R,
  2013ApJ...768..105M, 2015AA...578A..83G, 2015ApJ...798...28K,
  2016ApJ...829...33Y, 2016ApJ...833..222J}.  Determination of the AGN
luminosity function constrains models of the build-up of supermassive
black holes \citep{1982MNRAS.200..115S, 2004ApJ...602..603Y,
  2007ApJ...654..731H, 2008ApJ...679..118S, 2009A&A...493...55E,
  2000ApJ...531...42H, 2010MNRAS.401.2531A, 2013ApJ...773...14R,
  2014ApJ...787...73D, 2015MNRAS.448.3603D, 2015MNRAS.452..575S,
  2016MNRAS.462..190R}.  Due to the incidence of supermassive black
holes in most galaxies, the tight scaling relations observed to exist
between the mass of these black holes and properties of their host
galaxies, and the increasing consensus that AGN activity feeds back on
the host galaxy evolution, the AGN luminosity function also constrains
models of galaxy formation \citep{2006ApJ...650...42L,
  2008MNRAS.385.1846M}.  Finally, thanks to their relative brightness
and high Lyman-continuum (LyC) escape fractions, the luminosity
function of AGN determines their contribution to the radiation
background that influences the temperature and ionization state of the
intergalactic medium (IGM), possibly even primarily driving hydrogen
and helium reionization in the last twelve billion years
\citep{2012ApJ...746..125H, 2015AA...578A..83G, 2017ApJ...847L..15O,
  2018MNRAS.474.2904P, 2018arXiv180104931P}.

There is a renewed interest in understanding the evolution of the UV
luminosity function of AGN, triggered by the discovery of 19
low-luminosity ($-18.9>M_{1450}>-22.6$) AGN candidates between
redshifts $z=4.1$ and $6.3$ by \citet{2015AA...578A..83G} using a
novel X-ray/NIR selection criterion.  This finding suggested that if
100\% LyC escape fraction is assumed AGN brighter than $M_{1450}=-18$
can potentially produce all of the metagalactic hydrogen
photoionization rate inferred from the \lya forest at $4<z<6$, despite
the fact that these AGN are fainter than the brightest star-forming
galaxies at these redshifts.  (The UV luminosity function of galaxies
at $z=6$ has $M^*_{1450}\sim -20$.)  A significant presence of AGN at
high redshift ($z\sim 6$) and a dominant contribution of AGN to
reionization is appealing as the LyC escape fraction of galaxies is
uncertain.  High-redshift galaxies down to rest-frame UV magnitude
$M_\mathrm{UV}=-12.5$ ($L\sim 10^{-3}L^*$) at $z=6$
\citep{2017ApJ...835..113L} and redshifts up to $z=11.1$
\citep{2016ApJ...819..129O} have now been reported.  But the escape of
LyC photons has been measured in only a few comparatively bright
($L>0.5L^*$) galaxies at relatively low redshifts ($z < 4$).  The
escape fraction in these galaxies reveals a broad distribution from
less than 2\% to more than 80\% \citep{2010ApJ...725.1011V,
  2011ApJ...736...41B, 2015ApJ...804...17S, 2015ApJ...810..107M,
  2016A&A...585A..48G, 2017MNRAS.468..389J, 2018arXiv180506071S,
  2018arXiv180601741F, 2018arXiv180511621M, 2018arXiv180303655C}, but
the average escape fraction is typically lower than 20\%.  Statistical
constraints from \HI\ column density measurements in gamma-ray burst
(GRB) afterglow spectra suggest an even lower escape fraction of 0.5\%
\citep{2007ApJ...667L.125C, 2009ApJS..185..526F, 2018arXiv180507318T}.
This is a challenge for reionization models, which require an escape
fraction of about 20\% in galaxies as faint as $M_\mathrm{UV}=-13$
\citep{2016PASA...33...37F, 2015ApJ...802L..19R, 2016MNRAS.457.4051K}.
An enhanced incidence of high-redshift AGN may also be consistent with
the shallow bright-end slopes of the $z\sim 7$ UV luminosity function
of galaxies relative to a Schechter function
\citep{2012MNRAS.426.2772B, 2014MNRAS.440.2810B, 2014ApJ...792...76B,
  2015MNRAS.452.1817B} and the hard spectra of these galaxies
\citep{2015MNRAS.450.1846S, 2015MNRAS.454.1393S, 2017MNRAS.464..469S}.
Finally, AGN may also provide a natural explanation for the large
scatter in the \lya opacity between different quasar sightlines close
to redshift $z=6$ \citep{2015MNRAS.447.3402B, 2018arXiv180208177B}.
%% JFH Please cite new paper by eilers et al. here, not yet on archive. 
These opacity fluctuations extend to substantially larger scales
($\gtrsim 50\, h^{-1}$cMpc) than expected in galaxies-dominated
reionization models (\citealt{2015MNRAS.453.2943C}; although see
\citealt{2016MNRAS.460.1328D, 2015ApJ...813L..38D,
  2018arXiv180308932B}).  AGN clustering can result in these
fluctuations naturally if there is a significant contribution
($\gtrsim 50\%$) of AGN to the ionising emissivity at $z=5$--$6$
\citep{2017MNRAS.465.3429C}.

Several counter-arguments against a higher incidence of AGN at high
redshift have also been made. \citet{2017MNRAS.468.4691D} and
\citet{2018MNRAS.473.1416M} pointed out that an enhanced number
density of AGN at $z\sim 6$ can lead to a much earlier
\HeII\ reionization.  For instance, He~\textsc{ii} reionization is
complete at $z=4.5$ in the model of \citet{2015ApJ...813L...8M},
compared to $z=3$ in the standard scenario
\citep{2012ApJ...746..125H}.  Such early \HeII\ reionization will also
result in higher IGM temperatures due to the associated photoheating.
\citet{2017MNRAS.468.4691D} found that the temperature of the IGM at
mean density is twice as much in AGN-dominated reionization models as
the standard models at $z=3.5$--$5$, in conflict with constraints from
the \lya forest.  This inconsistency could be avoided by postulating a
reduced escape fraction of \HeII-ionizing photons in AGN, but it is
difficult to reconcile this with a unit escape fraction of
hydrogen-ionizing photons that is required to explain the Ly$\alpha$
opacity fluctuations.  Further arguments against AGN-dominated
reionization have been presented by \citet{2016MNRAS.459.2299F}, who
analysed the simulations of metal-line absorbers at $z\sim 6$.
\citet{2016MNRAS.459.2299F} find that in their cosmological radiation
hydrodynamical simulations AGN-dominated UV background results in too
many C~\textsc{iv} absorption systems relative to Si~\textsc{iv} and
C~\textsc{ii} at $z\sim 6$.  (However, note that these simulations
assume a $L_\nu\propto\nu^{-1.57}$ AGN SED at extreme UV
\citep{2002ApJ...565..773T}, which somewhat harder than recent
measurements ($L_\nu\propto\nu^{-1.7}$) by
\citet{2015MNRAS.449.4204L}.  \citet{2016MNRAS.459.2299F} found that,
relative to the the standard model \citep{2012ApJ...746..125H}, the
observed N(Si~\textsc{iv})/N(C~\textsc{iv}) column density ratio
measurements seem to require a harder and more intense $>4$~Ry
background.)  Finally, comparing the \citet{2015AA...578A..83G} sample
to X-ray-selected quasar data at $z=0$--$6$,
\citet{2017MNRAS.465.1915R} argued that the faint end of the AGN UV
luminosity function at $z\sim 6$ is probably shallower that that
reported by \citet{2015AA...578A..83G}.  \citet{2017MNRAS.465.1915R}
argue that the apparent contradiction with the results of
\citet{2015AA...578A..83G} could be explained by contamination from
the AGN host galaxies for faint AGN.

%---

A straightforward way towards a more robust understanding of AGN
contribution to reionization is to determine the evolution of the AGN
UV luminosity function.  However, many recent inferences of the
luminosity function suffer from inconsistencies arising from
inhomogeneous selection and mixing of AGN data.  This has resulted in
a large scatter in the inferred high-redshift hydrogen-ionizing AGN
emissivity between various recent studies.  For instance, there is an
order of magnitude scatter between various estimates of the
hydrogen-ionizing AGN emissivity at $z=5$--$6$
\citep{2011ApJ...728L..26G, 2012ApJ...755..169M, 2015AA...578A..83G,
  2018PASJ...70S..34A, 2018AJ....155..131M, 2018MNRAS.474.2904P,
  2017ApJ...847L..15O}.  Our aim in this paper is to address this
issue, by constructing an AGN sample with robust redshift and
completeness estimates and homogeneous assumptions of the cosmology
and intrinsic AGN spectrum.  We discuss our sample construction in
Section~\ref{sec:sample}.  Our derived luminosity functions are
presented in Section~\ref{sec:lf}.  Section~\ref{sec:reion} presents
our inference of the AGN contribution to hydrogen and helium
reionization.  We summarise our findings in Section~\ref{sec:conc}.

-- some people use photo-zs
-- some people mix binned data
-- some people fix slopes
-- some people exclude some data arbitrarily

@@

Our estimates for the double power law luminosity function are shown
in Figure~\ref{fig:mosaic} for 25 redshift bins.
%% JFH you are confusing terminology. posterior median and best-fit are not generally the same and you should
%% not refer to them as such. You are also not explaning what you mean by posterior median. Is this the
%% median of the individual marginalized posteriors? Or is it the median of the function that results from
%% the posterior distribution? Those are not generally the same, unless the model is linear in the parameters,
%% which it is not. Finally, best fit always means maximum likelihood, and that is certainly not what you are
%% plotting here, so don't say best-fit. You can say as our ``adopted model'' or ``fiducial model fit'' or
%% something like that. I would just explain waht you plot. 
The posterior median is shown as our adopted model at each redshift,
while the grey shaded region shows the one-sigma (68.26\%)
uncertainty\footnote{Throughout this paper, we adopt the posterior
  median and the equal-tailed 68.26\% credible interval as our model
  fit and its one-sigma uncertainty.}.  Consistent with previous
studies, the double power law model provides an excellent description
of the luminosity function model over almost the complete range of
redshifts spanned by the data.  It is only in the highest redshift bin
($z=5.5$--$6.5$) that the data show a weak preference for a single power law.
%% In
%% this bin, the resultant posterior distribution of the break magnitude
%% $M_*$ is bimodal with favoured values at the faint ($M_*>-18$) and
%% bright end of the data ($M_*<-30$).
While in the literature the
$z\sim 6$ AGN have been assumed to lie on the bright end of the
luminosity function \citep[e.g.,][]{2016ApJ...833..222J}, a comparison
with the luminosity function at lower redshifts ($z<5.5$) suggests
that these AGN should instead be understood to describe the faint-end
of a double power law.
%% JFH Okay so you need to be more clear here that what you mean is that the trend
%% from the plot is that M_star gets progressively brighter with redshift. This is not
%% obvious given what you write here. Indeed, it is not super obvious until one looks at FIgure 4, which
%% anyway has this prior already in it. 
Therefore, in light of the
low-redshift data, we use restricted priors in this
%% JFH Which redshift bin?? Make it more clear that this prior is put in to avoid bi-modal distributions
%% and it is informed by inspection of the lower redshift data. 
redshift bin: we
restrict the bright-end slope $\alpha$ to values less than $-4$,
%% JFH Something does not jive here, since the error bars you are showing on the high-z poitns cross
%% the -4 value of your prior? So either your prior is not a hard prior, or it is not exactly at -4
which
is equivalent to forcing $M_*$ to be at the bright end of the data.
Other parameters continue to have wide uniform priors.  This also
illustrates the importance of analysing the evolution of the QLF with
redshift.

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small_global.pdf}
    % mosaic_selected.py and drawlf_selected.py 
  \end{center}
  \caption{Luminosity function estimates from $z=0.6$ to $6.5$.
    Similar to Figure~\ref{fig:mosaic}, the symbols show our inferred
    binned luminosity functions.  In each redshift bin, yellow curves
    show our fiducial double power law luminosity function model in
    that redshift bin.  Other curves show the three global evolution
    models.  Shaded regions show the one-sigma (68.26\%)
    uncertainties.}
  \label{fig:mosaic_global}
\end{figure*}
